---
title: "Stand-Alone Thai R Markdown Setup"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/alone.Rmd")
library(here)

```


### Plan

2 Mains Wrapper:

-  `thaipdf_document()`: for wrapping `rmarkdown::pdf_document()`
-  `bookdown::pdf_book()`: for wrapping `bookdown::pdf_book()`


```{r}
usethis::use_r("thaipdf")
```



## 1. Thai PDF Document — Wrap `rmarkdown::pdf_document()`


```{r thaipdf_document}
thaipdf_document <- function(...) {
  rmarkdown::pdf_document(
    latex_engine = "xelatex",
    includes = rmarkdown::includes(
      in_header = thai_preamble(),
      before_body = before_body()
    ),
    ...
  )
}
```



### Helper: Find path to Global Preamble & Before body

`thai_preamble()` = return path to global thai-preamble.tex

`before_body()` = return path to before_body which contains \sloppy


```{r thai_preamble}
thai_preamble <- function(){
  thaipdf_paths()[["path_pre_global"]]
}

thai_preamble()
```


```{r before_body}
before_body <- function(){
  thaipdf_paths()[["path_before_body"]]
}

before_body()
```






## 2. THai PDF Book — Wrap `bookdown::pdf_book()`

```{r thaipdf_book}
thaipdf_book <- function(...) {

  # Check bookdown
  if (!requireNamespace("bookdown")) {
    cli::cli_alert_warning("This function require package {.pkg bookdown} installed.")
    cli::cli_li("To install run {.code install.packages('bookdown')}")
  }

  bookdown::pdf_book(
    base_format = thaipdf::thaipdf_document,
    ...
  )
}
```

Test if `{bookdown}` is not installed.

```{r}
if(!requireNamespace("bookdown")){
  cli::cli_alert_warning("This function require package {.pkg bookdown} installed.")
  cli::cli_li("To install run {.code install.packages('bookdown')}")
}
```

## HowTo
### Howto: `pdf_document` and `includes()`

```{r}
rmarkdown::includes()
```

```{r}
rmarkdown::pdf_document()
```

