---
title: "Stand-Alone Thai R Markdown Setup"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/alone.Rmd")
library(here)

```


### Plan

2 Mains Wrapper:

-  `thaipdf_document()`: for wrapping `rmarkdown::pdf_document()`
-  `bookdown::pdf_book()`: for wrapping `bookdown::pdf_book()`


```{r}
usethis::use_r("thaipdf")
```





## 1. Thai PDF Document — Wrap `rmarkdown::pdf_document()`

### New 

**Steps**

1. Render a temporary file from template-thai-preamble.tex with option 

-  `thai_font`
-  `line_spacing`

use `rmarkdown::pandoc_template()`

2. Run `rmarkdown::pdf_document` that `includes` temp thai-preamble and before_body


```{r thaipdf_document}
thaipdf_document <- function(thai_font = "TH Sarabun New", 
                             line_spacing = 1.5,
                             ...
                             ) {
  
  # Render a tmp file from template-thai-preamble.tex
  tmp_preamble <- tempfile("thai-preamble-", fileext = ".tex")
  # Write pandoc template to a location with variable substitution 
  tmp_preamble <- write_thai_preamble(path_abs = tmp_preamble, 
                                    thai_font = thai_font, 
                                    line_spacing = line_spacing)
  # Clean up when function exit
  ## See: https://stackoverflow.com/questions/28300713/how-and-when-should-i-use-on-exit
  on.exit(unlink(tmp_preamble), add = TRUE)
  
  rmarkdown::pdf_document(
    latex_engine = "xelatex",
    includes = rmarkdown::includes(
      in_header = tmp_preamble,
      before_body = before_body()
    ),
    ...
  )
}
```

```{r}
tempfile("thai-preamble-", fileext = ".tex")
```

```{r}
{print("hello"); Sys.sleep(2); print("World")}
```

```{r}
j06 <- function(x) {
  cat("Hello\n")
  on.exit({Sys.sleep(1); cat("Goodbye!\n")}, add = TRUE)
  
  if (x) {
    return(10)
  } else {
    stop("Error")
  }
}

j06(10)
```


### Old 

```{r thaipdf_document2}
thaipdf_document2 <- function(...) {
  rmarkdown::pdf_document(
    latex_engine = "xelatex",
    includes = rmarkdown::includes(
      in_header = thai_preamble(),
      before_body = before_body()
    ),
    ...
  )
}
```





### Helper: Find path to Global Preamble & Before body

`thai_preamble()` = return path to global thai-preamble.tex

`before_body()` = return path to before_body which contains \sloppy


```{r thai_preamble}
thai_preamble <- function(){
  thaipdf_paths()[["path_pre_global"]]
}

thai_preamble()
```


```{r before_body}
before_body <- function(){
  thaipdf_paths()[["path_before_body"]]
}

before_body()
```






## 2. THai PDF Book — Wrap `bookdown::pdf_book()`

```{r thaipdf_book}
thaipdf_book <- function(...) {

  # Check bookdown
  if (!requireNamespace("bookdown")) {
    cli::cli_alert_warning("This function require package {.pkg bookdown} installed.")
    cli::cli_li("To install run {.code install.packages('bookdown')}")
  }

  bookdown::pdf_book(
    base_format = thaipdf::thaipdf_document,
    ...
  )
}
```

Test if `{bookdown}` is not installed.

```{r}
if(!requireNamespace("bookdown")){
  cli::cli_alert_warning("This function require package {.pkg bookdown} installed.")
  cli::cli_li("To install run {.code install.packages('bookdown')}")
}
```

## HowTo
### Howto: `pdf_document` and `includes()`

```{r}
rmarkdown::includes()
```

```{r}
rmarkdown::pdf_document()
```

