---
title: "Build"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/build.Rmd")
library(here)
```

# Release PKG

## Version

```{r}
usethis::use_dev_version()
```

```{r}
usethis::use_version("patch")
usethis::use_version("minor")
```

## Github Release

```{r}
usethis::use_github_release()
```



# 1. Git & Build

```{r use_git}
usethis::use_git()
```

## Git Ignore

```{r use_git_ignore}
usethis::use_git_ignore("*.nb.html") # Ignore dev/ html_notebook
# usethis::use_git_ignore("testdata/") # ignore private Test Data in `inst/testdata`
```
## Build Ignore

May be not ignore dev/ ?

```{r use_build_ignore}
usethis::use_build_ignore("dev")
```

## Github Links

```{r}
usethis::use_github_links()
```

## Github Action

```{r}
usethis::use_github_actions()
```


## Test coverage workflow

1. Call `usethis::use_coverage()`

```{r}
# usethis::use_coverage()
```

2. Set github action

```{r}
use_github_action("test-coverage")
```

[Ref](https://github.com/r-lib/actions/tree/v1/examples#test-coverage-workflow)

this will connect your package to codecov.

```{r}
covr::codecov(token = "")
```


3. Package Coverage (Local)

```{r}
covr::package_coverage()
```

for interactive use

```{r}
covr::report()
```





# 2. DOCs


## DESCRIPTION

```{r DESCRIPTION}
usethis::use_description(
fields = list(
  Title = "R Markdown for PDF in Thai language",
  `Authors@R` = 'person("Kittipos", "Sirivongrungson", 
                        email = "ki11ip0.s.a.s@gmail.com", 
                        role = c("aut", "cre"))',
  Description = "Provide R Markdown templates and LaTeX preamble which is necessary for creating PDF in Thai language.",
  License = "MIT + file LICENSE",
  Depends = "R (>= 4.0.0)"
  )
)
```


## LICENSE

```{r LICENSE}
usethis::use_mit_license()
```

## Logo

```{r}
usethis::use_logo("man/figures/logo.png")
```


## README

```{r README}
usethis::use_readme_rmd()
```



```{r}
usethis::use_lifecycle_badge("experimental")
# usethis::use_lifecycle_badge("deprecated")
```

## NEWS

```{r}
usethis::use_news_md()
```


## Article

```{r}
usethis::use_article("thaipdf")
```

Images folder

```{r}
fs::dir_create(here("vignettes/articles/img"))
```



# 3. Dependencies

## Import

```{r import}
# usethis::use_pipe()
usethis::use_package("fs")
usethis::use_package("cli")
usethis::use_package("rmarkdown")
usethis::use_package("bookdown", type = "Suggests")
```




## Import from

```{r import_from}
# usethis::use_import_from("rlang", ":=") # Must have if use rlang
```

## Global variables


```{r globalVariables}
# Put this in  R/globals.R
# utils::globalVariables(c("var1"))
# usethis::use_r("globals.R")
```

# 4. Tests

```{r testthat}
usethis::use_testthat()
```

Helper Functions for test -> create `testthat/helper.R` manually


If you want to use data for testing, put data file(s) in `inst/testdata`.
The path to this data can be obtained by `system.file("testdata",...,package="my_package")`.

For example, If I put `cars.csv` in `inst/testdata`, to read into R use this command `read.csv(system.file("testdata","cars.csv", package="my_package"))`.

[ref](https://stackoverflow.com/questions/32328802/where-should-i-put-data-for-automated-tests-with-testthat)


**Path to testdata folder**: put this in `testthat/test-helper.R`:

```{r path_testdata}
path_testdata <- function(..., package = "pkg_name") {

  system.file("testdata", ... ,package = package)

}
```


# 5. Data

## Exported Data

-   Run: `usethis::use_data(export_df)`

To store exported data in `data/`. 
Each file in this directory should be `.rda` file containing a single object.

-   Run: `usethis::use_data_raw("export_df")`

To store code that used for data preparation in `data-raw/` 


```{r export_data}
# usethis::use_data(export_df1,export_df2) 

# usethis::use_data_raw("export_df1") # Code to Prepare data
# usethis::use_data_raw("export_df2") # Code to Prepare data
```

**How to Document a Data set**

Document the name of the data in `R/` as roxygen2:

```{r data_doc_example}
#' Prices of 50,000 round cut diamonds.
#'
#' A dataset containing the prices and other attributes of almost 54,000
#' diamonds.
#'
#' @format A data frame with 53940 rows and 10 variables:
#' \describe{
#'   \item{price}{price, in US dollars}
#'   \item{carat}{weight of the diamond, in carats}
#'   ...
#' }
#' @source \url{http://www.diamondse.info/}
"diamonds"
```




## Internal Data

Save all of the objects for internal use in `R/sysdata.rda.`
Usually, they don’t need to be documented.

```{r internal_data}
# usethis::use_data(df1, df2, df3, internal = TRUE)
```



