---
title: "thaipdf config"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/config.Rmd")
library(here)
library(cli)
library(dplyr)
library(testthat)
```

```{r}
usethis::use_r("config")
usethis::use_test("config")
```

### Check which PKG is Active

```{r}
fs::path_package("thaipdf") 
```

### Config Parameters

`thai_font`: thai language font
`line_spacing`: line spacing (default = 1.5)

TO ADD

`par_indent`: paragraph indent (default = `NULL`)
`par_spacing`: paragraph spacing (default = `NULL`)



## Setting Config

`thaipdf_config_set()`:

render USER-based `thai-preamble` in `rmarkdown/` and `pre-tex/` folder from template `template-thai-preamble.tex` with metadata from `config.yml`

args: `thai_font`

```{r thaipdf_config_set}
thaipdf_config_set <- function(thai_font = "TH Sarabun New", line_spacing = 1.5){
  
  # Validate Metadata
  thaipdf_config_validate(thai_font = thai_font, line_spacing = line_spacing)
  # Metadata: Named List as Pandoc Var
  metadata <- list(thai_font = thai_font, line_spacing = line_spacing)
    
  # All relevant file paths in PKG
  paths <- thaipdf_paths()
  ## Template Path
  paths_temp <- paths[["path_temp"]]
  
  ## Output Paths (UPDATE HERE)
  paths_out <- list(
    paths[["path_pre_global"]],
    paths[["path_pre_proj"]]
    )
  
  # Write config.yml
  yaml::write_yaml(metadata, file = paths[["path_config"]])
  
  # Render to all output: thai-preamble.tex
  for (i in seq_along(paths_out)) {
    rmarkdown::pandoc_template(
      metadata = metadata,
      template = paths[["path_temp"]],
      output = paths_out[[i]]
    )
  }
  # Display Message
  cli::cli_alert_success("Setting thaipdf global configuration")
  thaipdf_config_get()

}

thaipdf_config_set()
```

### Validate Metadata

```{r thaipdf_config_validate}
thaipdf_config_validate <- function(thai_font = "TH Sarabun New", 
                                    line_spacing = 1.5
                                    ){
    
  # Validate Thai font
  is_valid_font <- all(is.character(thai_font), length(thai_font) == 1, (thai_font != ""))
  if(!is_valid_font) stop("`thai_font` is invalid. You must provide only 1 valid Thai font name.", call. = FALSE)
  
  # Validate Line Spacing
  is_valid_lin_sp <- all(is.numeric(line_spacing), length(line_spacing) == 1, line_spacing > 0)
  if(!is_valid_lin_sp) stop("`line_spacing` is invalid. You must provide a numeric value.", call. = FALSE)
  
  
  
}

thaipdf_config_validate()
thaipdf_config_validate(1)
thaipdf_config_validate(line_spacing = "a")
```
#### Tes: Validation

```{r}
testthat::test_that("thaipdf_config_set() works",{
  
  # Error Test
  expect_error(thaipdf_config_set(thai_font = ""))
  expect_error(thaipdf_config_set(thai_font = c("a", "b")))
  expect_error(thaipdf_config_set(thai_font = 1))

})
```



Test Validation

```{r}
thai_font <- c(NULL)
is_valid <- all(is.character(thai_font), length(thai_font) == 1, (thai_font != ""))
is_valid
rm(is_valid)
```


```{r}
ft <- "ABC"
cli_alert_success("Setting thaipdf configuration")
cli::cli_li("Set Thai font to {.val {ft}}")
rm(ft)
```



## Getting Config

`thaipdf_config_get()`: read `config.yml` and print to console nicely

```{r thaipdf_config_get}
thaipdf_config_get <- function(){
  
  path_config <- fs::path_package("thaipdf", "templates", "config.yml")
  ## Read YAML
  config_ls <- suppressWarnings(yaml::read_yaml(file = path_config))
  ## Add class "thaipdf_config
  new_thaipdf_config(config_ls)
  
}

thaipdf_config_get()
```

To get list value

```{r}
l <- thaipdf_config_get()
unclass(l)

rm(l)
```



### Print Method: `thaipdf_config_get`

```{r print.thaipdf_config}
print.thaipdf_config <- function(x, ...){
  
  th_font <- x[["thai_font"]]
  cli::cli_h2("thaipdf Global Setting")
  cli::cli_li("Thai font setting is {.val {th_font}}")
  cli::cli_li("Line spacing is {.val {line_spacing}}")
  invisible(x)
}

print(thaipdf_config_get())
```

testing

```{r}
ft <- "ABC"
cli::cli_h2("thaipdf Global Setting")
cli::cli_li("Thai font setting is {.val {ft}}")
rm(ft)
```



If YAML field empty return `NULL`

```{r}
list(a = NULL, b=1) %>% is.null()
list(a = NULL, b=1)$a %>% is.null()
```


