---
title: "CRAN Preparation"
author: "kittipos sirivongrungson"
date: '2022-03-31'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/cran.Rmd")
library(here)

```

Referece

1. [Release a PKG Chaper](https://r-pkgs.org/release.html)
2. [Prepare for CRAN from ThinkR](https://github.com/ThinkR-open/prepare-for-cran)

## Badges

```{r}
usethis::use_cran_badge()
```


## General Check

- Check DESCRIPTION File


## CRAN comments 

```{r}
usethis::use_cran_comments()
```

## Run Tests & Examples

```{r}
# Run tests and examples
devtools::test()
devtools::run_examples()
```


## R CMD Check as CRAN


There will always be one NOTE when you first submit your package.

```{r}
rhub::platforms()
```

Run this

```{r}
cran_prep <- rhub::check_for_cran()
cran_prep$cran_summary()
```


```{r}
# Check package as CRAN
rcmdcheck::rcmdcheck(args = c("--no-manual", "--as-cran"))
```


## Check Other Distro

**_rhub**

```{r}
devtools::check_rhub()
```

> checking for detritus in the temp directory ... NOTE
  Found the following files/directories:
    'lastMiKTeXException'
    
### Check Windows    

```{r}
rhub::check_on_windows(path = here("."),
                       check_args = "--force-multiarch")
```
Pass

```{r}
devtools::check_win_devel()
```

### Check Linux

```{r}
rhub::check_on_solaris(path = here("."))
```

**Fail on solaris**

Error: pandoc document conversion failed with error 1
     Backtrace:
         ▆
      1. └─thaipdf:::write_thai_preamble(tmp_file) at test-write_thai_preamble.R:6:2
      2.   └─rmarkdown::pandoc_template(...)
      3.     └─rmarkdown::pandoc_convert(...)
      4.       └─rmarkdown:::stop2(...)

But on ubantu using github action pass ??



## LICENSE

Complicated topic 

Thai LaTeX preamble code, I reference the author as copyright holder (cph) in `DESCRIPTION` and included explanation in `LICENSE.note`.

See [write R extension LICENSES](https://cran.r-project.org/doc/manuals/r-release/R-exts.html#The-DESCRIPTION-file)




# Misc Check

## Spell Check

thaipdf use Thai language, so It can't spelle check.

However I added 

```
Language: th, en-US
```
to the DESCRIPTION

```{r}
# Check spelling
# usethis::use_spell_check()
# spelling::spell_check_package()
```

## Check URL

```{r}
# Check URL are correct
# remotes::install_github("r-lib/urlchecker")
urlchecker::url_check(here("."))
```

# Release

```{r}
# devtools::release()
```


