---
title: "Planning for thaipdf"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("my_dev/plan.Rmd")
library(here)
```

Nomenclatures: DEV (for developer), USER (for user)

## Package Structure

-   **inst/**

    -   **rmarkdown/**

        -   Thai PDF R Markdown

        -   Thai PDF R Markdown (with preamble)

            -   Rmd
            -   preTeX/ thai-preamble.tex

    -   **templates/**

        -   config.yml
        -   template-thai-preamble.tex

    -   **preTeX/**

        -   thai-preamble.tex
        -   before_body.tex

### Create Structures

**templates/**

```{r}
fs::file_create(here("inst/templates/config.yml"))
fs::file_create(here("inst/templates/template-thai-preamble.tex"))
```

**preTeX/**

```{r}
fs::dir_create(here("inst/preTeX"))
```

**rmarkdown/**

thai-pdf-rmd-w-pre/

- preTeX/

```{r}
# usethis::use_rmarkdown_template(
#   template_name = "Thai PDF R Markdown (with preamble)",
#   template_description = "R Markdown PDF template with LaTeX preamble file that supports Thai language.",
#   template_create_dir = TRUE
# )
```

thai-pdf-rmd/

```{r}
usethis::use_rmarkdown_template(
  template_name = "Thai PDF R Markdown",
  template_dir = "thai-pdf-rmd"
  template_description = "R Markdown PDF stand-alone template that supports Thai language.",
  template_create_dir = FALSE
)
```





thai-pdf-book/


```{r}
usethis::use_rmarkdown_template(
  template_name = "Thai PDF Bookdown",
  template_dir = "thai-pdf-book",
  template_description = "R Markdown PDF stand-alone template using Bookdown that supports Thai language.",
  template_create_dir = FALSE
)
```




### Paths to Files


```{r}
usethis::use_r("path")
usethis::use_test("path")
```


`th_pre`= Thai preamble file name

```{r thaipdf_paths}
thaipdf_paths <- function(th_pre = "thai-preamble.tex") {

  ## Template file name
  temp_filename <- paste0("template-", th_pre)

  # Input Path
  ## Template path
  path_temp <- fs::path_package("thaipdf", "templates", temp_filename)
  ## config.yml path
  path_config <- fs::path_package("thaipdf", "templates", "config.yml")

  # Output Path
  ## Global Preamble at PreTeX/
  path_pre_global <- fs::path_package("thaipdf", "preTeX", th_pre)
  ## Global PreTeX/before_body.tex for \sloppy macro
  path_before_body <- fs::path_package("thaipdf", "preTeX", "before_body.tex")
  ## At rmarkdown/
  ### Thai PDF with Preamble (for Project)
  path_pre_proj <- fs::path_package("thaipdf", "rmarkdown", "templates",
                                   "thai-pdf-rmd-w-pre", 
                                   "skeleton", "preTeX", th_pre)


  list(
    path_temp = path_temp,
    path_config = path_config,
    path_pre_global = path_pre_global,
    path_before_body = path_before_body,
    path_pre_proj = path_pre_proj
  )
}

thaipdf_paths()
```

#### Howto: Find Paths

```{r}
fs::path_package("thaipdf")
# File
## Input Template File Name
paste0("template-",file_names$th_pre)
## Output TeX Preamble File Name
file_names$th_pre

# Path
## Input Location path
fs::path_package("thaipdf", "templates", paste0("template-", file_names$th_pre))
## Input Metadata path
fs::path_package("thaipdf", "templates", "config.yml")

# Output Location
## preTeX/
fs::path_package("thaipdf", "preTeX")
## rmarkdown/
### Thai PDF with Preamble
fs::path_package("thaipdf", "rmarkdown", "templates", "thai-pdf-rmd-w-pre", 
                 "skeleton", "preTeX", "thai-preamble.tex")
```



## OOP

**thaipdf_config**

-   attributes: "attr_name" = description

### Class Functions (DEV)

**thaipdf_config**

-   `create_*`: create "class_name" & set ... attribute
-   `new_thaipdf_config`: add "thaipdf_config" class to existing list 
-   `is_thaipdf_config`: check class

### Method: 

**thaipdf_config**

-   `print.thaipdf_config()`: print `thaipdf_config` object nicely to console


## Plan: USER functions

1.  `use_thai_preamble()`: create PROJECT-based `thai-preamble.tex` from template `template-thai-preamble.tex`

2.  `thaipdf_config_set()`: render USER-based `thai-preamble` in `rmarkdown/` and `preTeX/` folder from template `template-thai-preamble.tex` with metadata from `config.yml`

3.  `thaipdf_config_get()`: read `config.yml` and print to console nicely

## Plan: ... functions Family

1.  `fun1`:

2.  `fun2`:
