---
title: "Use Thai Preamble Template"
output: 
  html_notebook
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/pre-temp.Rmd")
library(here)
library(usethis) 
library(cli)
```

**Goal:** Give user a `thai-preamble.tex` file to specified location to use in the project as they like.

```{r}
usethis::use_r("use_thai_preamble")
usethis::use_test("use_thai_preamble")
```


### Examples

```{r}
if (FALSE) {
  # Running this will write `thai-preamble.tex` to your working directory
  use_thai_preamble()
  # Write `thai-preamble.tex` under preTeX/ directory
  use_thai_preamble(name = "preTeX/thai-preamble.tex")
  # Specify Thai font to use
  use_thai_preamble(thai_font = "Laksaman")
}
```


### Fun: `use_thai_preamble()`

`use_thai_preamble()`: create PROJECT-based `thai-preamble.tex` from template `template-thai-preamble.tex`

Not Require Usethis PKG

User may **overide global setting** by input metadata to  `rmarkdown::pandoc_template` 



```{r use_thai_preamble}
use_thai_preamble <- function(name = "thai-preamble.tex",
                              thai_font = "TH Sarabun New",
                              open = FALSE,
                              overwrite = FALSE
                              ){
  
    ### Build path
    name_clean <- fs::path(fs::path_ext_remove(name), ext = "tex")
    out_path <- fs::path_wd(name_clean)
    out_name <- fs::path_file(out_path)
    ### If file already exist, not overwrite unless instructed to do so.
    is_file_exist <- fs::file_exists(out_path)
    if (is_file_exist && !overwrite) {
      cli::cli_alert_danger("file {.val {out_path}} already exist, to overwrite set {.code overwrite = TRUE}")
      return(invisible(NA_character_))
    }
  
  # Validate Metadata
  thaipdf_config_validate(thai_font = thai_font)
  # Metadata: Named List as Pandoc Var
  metadata <- list(thai_font = thai_font)
  
  # All relevant file paths in PKG
  paths <- thaipdf_paths()
  ## Template Path
  paths_temp <- paths[["path_temp"]]
  
  # Main Engine:
  ## Render to Output at Specified Location
  write_path <- rmarkdown::pandoc_template(
      metadata = metadata,
      template = paths[["path_temp"]],
      output = out_path
  )
  # Info to Console
  cli::cli_alert_success("Writing {.val {out_name}} at {.file {write_path}}")
  cli::cli_alert_success("Thai font was set to {.val {thai_font}} in the preamble.")
  
  # Inform what TODO
  ui_inform_yaml(name_clean)
  
  if (open) {
    fs::file_show(write_path)
  }  
  # Return Path of Output file
  invisible(write_path)
  
}

use_thai_preamble(name = "my_data/something", 
                  thai_font = "Sarabun", 
                  overwrite = TRUE, open = F)
```





```{r}
name <- "asdf"
thai_font <- "sdfasdf"
cli::cli_alert_danger("file {.file {name}} already exist, to overwrite set {.code overwrite = TRUE}")


cli::cli_alert_success("Writing {.val {name}}")
cli::cli_alert_success("Thai font was set to {.val {thai_font}} in the preamble.")

rm(name, thai_font)
```







### YAML inform Code Block


```{r ui_inform_yaml}
#' Print what TODO about R Markdown YAML to the R console
#'
#' @param in_header Text to `in_header` fields of YAML
#'
#' @return A character
ui_inform_yaml <- function(in_header = "path-to-preamble.tex") {
  
  par_end <- function(){ cli::cli_par(); cli::cli_end() }
  
  cli::cli_h1("TODO")

  cli::cli_text("For YAML header of R Markdown in {.code pdf_document:} or {.code bookdown::pdf_document2:}")
  cli::cli_li("Set {.code latex_engine} to {.code xelatex}")
  cli::cli_li("Set to include the path to LaTeX preamble")

  par_end()

  cli::cli_rule(left = "Like This")

  # cat("    latex_engine: xelatex
  #   includes:
  #     in_header:", in_header)
  # cat("\n")
  message("    latex_engine: xelatex
    includes:
      in_header:", "foo.tex")
  message("\n")

  cli::cli_rule()
  
  par_end()
  
  cli::cli_li("Add LaTeX macro {.code \\sloppy} to the beginning of the body of R Markdown (just after YAML header).")
  
  par_end()
  
  cli::cli_text("{.strong For more details see}")
  cli::cli_li("How to include preamble in R Markdown {.url https://bookdown.org/yihui/rmarkdown-cookbook/latex-preamble.html}")
  cli::cli_li("LaTeX setting in Thai {.url http://pioneer.netserv.chula.ac.th/~wdittaya/LaTeX/LaTeXThai.pdf}")
  
}

ui_inform_yaml()
```




Cat vs Message is the same


```{r}
  cat("    latex_engine: xelatex
    includes:
      in_header:", "foo.tex")
  cat("\n")
```

```{r}
  message("    latex_engine: xelatex
    includes:
      in_header:", "foo.tex")
  message("\n")
```


### HowTo

#### Howto: YAML

Desired message 

```{yml}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex 
    includes:
      in_header: "file" 
```


```{r}
cli_h1("TODO")


cli_text("For YAML header of R Markdown in {.code pdf_document:} or {.code bookdown::pdf_document2:}")
cli_li("Set {.code latex_engine} to {.code xelatex}")
cli_li("Set to include the path to LaTeX preamble")

cli_par()
cli_end()

cli_rule(left = "Like This")

usethis::ui_code_block("
    latex_engine: xelatex 
      includes:
        in_header: \"file\"
", copy = F)

cli_rule()
cli_text("For more details see {.url https://bookdown.org/yihui/rmarkdown-cookbook/latex-preamble.html}")
```


```{r}
ui_info("Make sure to set YAML header of the R Markdown file as.")

ui_code_block("
output:
  bookdown::pdf_document2:
    latex_engine: xelatex 
    includes:
      in_header: \"file\"
", copy = F)

ui_line("Or")

ui_code_block("
output:
  pdf_document:
    latex_engine: xelatex 
    includes:
      in_header: \"file\"
", copy = F)
```


```{r}
cli_li("A piece of code: {.code sum(a) / length(a)}")
ui_line("A piece of code: {ui_code('sum(a) / length(a)')}")
```


#### Howto: File Stuff

```{r}
fs::file_exists("thai-preamble.tex")
fs::file_access("thai-preamble.tex",mode = "execute")
file.exists("thai-preamble.tex")

fs::path(fs::path_ext_remove("file.tex"), ext = "tex")
```

```{r}
fs::file_exists("./my_dev/pre-temp.nb.html")

file.exists("./my_dev/pre-temp.nb.html")
```




#### How to: ui_*() function from Usethis

```{r}
cli::cli_alert_danger("asdf") 
```


```{r}
file_ex <- "file.tex"
th_font_ex <- "TH Sarabun New"
## Set fonts
usethis::ui_line("  - Set Thai font as {usethis::ui_value(th_font_ex)}")
cli_li("Set Thai font as {.val {th_font_ex}}") # better
## Font is
usethis::ui_line("  - Thai font is {usethis::ui_value(th_font_ex)}")

## Warning
usethis::ui_stop("file {usethis::ui_value(file_ex)} already exist, to overwrite set {usethis::ui_code('overwrite = TRUE')}")

### File Not change
usethis::ui_info("File {usethis::ui_value(file_ex)} has not changed")
usethis::ui_done("Checking {usethis::ui_value(file_ex)}")
```

```{r}
cli_text("Some random numbers: {.val {runif(4)}}.")
cli_text("  - Set Thai font as {.val {th_font_ex}}")
```


```{r}
ui_todo("Redocument with {ui_code('devtools::document()')}")
ui_stop("file {usethis::ui_value(ff)} already exist, to overwrite set {usethis::ui_code('overwrite = TRUE')}")

ui_done("blah")
usethis::ui_code("overwrite = TRUE")
```


