---
title: "Improving use_thai_preamble()"
author: "kittipos sirivongrungson"
date: '2022-03-20'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/use-th-pre-impr.Rmd")
library(here)

```

### Desired Behavior of `use_thai_preamble()`

Relative to WD

- `use_thai_preamble("some_file")` : some_file at current wd -> Works
- `use_thai_preamble("../some_file")` : 1 level up -> Works
- `use_thai_preamble("out/some_file")` : 1 level down -> Works

Create at arbitrary location 

- `use_thai_preamble("~/new_file")` or `use_thai_preamble("/../../new_file")`

We need to test `rmarkdown::pandoc_template()`

- `template` and `output` args only accept ABSOLUTE path

plan using `fs::path_abs()` to wrap `output` since, it accept both relative path to WD and absolute path

```{r}
getwd()
```

Works

```{r}
rmarkdown::pandoc_template(
  metadata = list(thai_font = "Somefonts", line_spacing = 2),
  template = thaipdf:::thaipdf_paths()[["path_temp"]],
  # To Relative Location to WD
  output = fs::path_abs("dev/test_data/test-thai-preamble.tex")
  )
```

Works 

```{r}
# rmarkdown::pandoc_template(
#   metadata = list(thai_font = "Somefonts", line_spacing = 2),
#   template = thaipdf:::thaipdf_paths()[["path_temp"]],
#   # To Absolute Location 
#   output = fs::path_abs("/Users/kittipos/my_pkg/test-thai-preamble.tex")
#   )
```

### HowTo: Write Template to Temp file

```{r}
tmpdir <- tempdir()

file.path(tempdir(), "thai-preamble.tex")
```

```{r}
# the same
fs::file_show(tmpdir)
fs::file_show(tempdir())
```





```{r}
rmarkdown::pandoc_template(
  metadata = list(thai_font = "Somefonts", line_spacing = 2),
  template = thaipdf:::thaipdf_paths()[["path_temp"]],
  # To Relative Location to WD
  output = fs::path_abs(file.path(tempdir(), "thai-preamble.tex"))
  )

# fs::file_show(tempdir())
fs::file_exists(file.path(tempdir(), "thai-preamble.tex"))
```

```{r}
tmp_file <- file.path(tempdir(), "thai-preamble.tex")

thaipdf::use_thai_preamble(tmp_file)

fs::file_exists(tmp_file)
# fs::file_show(tempdir())
#unlink(tmp_file)
```

```{r}
.old_wd <- setwd(tempdir())

thaipdf::use_thai_preamble()

fs::file_exists("thai-preamble.tex")
#fs::file_show("thai-preamble.tex")
unlink("thai-preamble.tex")
setwd(.old_wd)
```

```{r}
.old_wd <- setwd(tempdir())

thaipdf::use_thai_preamble()
```

